Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-09 exp1/iswc2013.tex
we can do t-test on 32
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@546 43ef1190-90fd-4dd7-a769-d0121f02b80e

The resulting normal plot is in figure~\ref{fig:frac32normal}. We see that
only two main effects are significant on a $\alpha = 0.05$ level
according to the Lenth criterion, ``Implement'' is again deemed a
significant improvement, and ``Union'' is deemed significantly the
hardest operation for the query engine. We see that some other points
also deviate from the straight line, but with as few runs as this, the
total variance is great, so no other conclusions can be drawn. Also,
the Student's t-test we used in the previous section cannot be
employed, as we have no additional data to use for the
test.\todo{actually, we can}

>>>>

The resulting normal plot is in figure~\ref{fig:frac32normal}. We see
that only two main effects are significant on a $\alpha = 0.05$ level
according to the Lenth criterion, ``Implement'' is again deemed a
significant improvement, and ``Union'' is deemed significantly the
hardest operation for the query engine. We see that some other points
also deviate from the straight line, but with as few runs as this, the
total variance is great, so no other conclusions can be drawn. We may
use the t-test we used in the previous section, as we have only two
active factors and so we may treat it as a $2^2$ experiment with 8
repetitions, but we must expect a higher p-value due to the larger
variance.
